### 2021-09-15 sections/appendix/descrete_event_simulation/main.tex
Compile main.pdf after rebase
Make sure checks pass
- Update known words for apell spellcheck
- Add proselint expected_errors

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of parking queue
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % the vertical lines of parking queue
        \foreach \i in {1,...,4, 7.1}
            \draw (3cm-\i*12pt,0) -- +(0,-1.5cm);

@@

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
            \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the very start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

@@

To eliminate any stochasticity in the simulation, the simulation can be run
numerous times and get the avergae performance measures out of all the runs.

>>>>

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of parking queue
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % the vertical lines of parking queue
        \foreach \i in {1,...,4, 7.1}
            \draw (3cm-\i*12pt,0) -- +(0,-1.5cm);

@@

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
            \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

@@

To eliminate any stochasticity in the simulation, the simulation can be run
numerous times and get the average performance measures out of all the runs.
